---
title: "Airbnb"
author: "Shengqian Wang, Watson Xin Wang"
date: 2023-12-11
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
```


# 1 Introduction



# 2 Data Manipulation and Visualization

## 2.0 Set up

```{r , include=FALSE}

# You can set some global options for knitting chunks

knitr::opts_chunk$set(echo = TRUE)

# Load some libraries

library(tidyverse)
library(tidycensus)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot) # plot correlation plot
library(corrr)      # another way to plot correlation plot
library(kableExtra)
library(broom)
library(tufte)
library(rmarkdown)
library(jtools)     # for regression model plots
library(ggstance) # to support jtools plots
library(ggpubr)    # plotting R^2 value on ggplot point scatter
library(broom.mixed) # needed for effects plots
library(stargazer)

# functions and data directory
root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

palette4 <- c("#005B96", "#FFD700", "#E63946", "#F0F0F0")
palette5 <- c("#005B96", "#FFD700", "#E63946", "#2A9D8F", "#F0F0F0")
palette6 <- c("#005B96", "#FFD700", "#E63946", "#2A9D8F", "#264653", "#F0F0F0")
palette7 <- c("#005B96", "#FFD700", "#E63946", "#2A9D8F", "#264653", "#E76F51", "#F0F0F0")
palette8 <- c("#005B96", "#FFD700", "#E63946", "#2A9D8F", "#264653", "#E76F51", "#F4A261", "#F0F0F0")

```

## 2.1 Data Wrangling

### 2.1.1 Data loading

#### (1) Load Airbnb dataset

```{r read_data,results = FALSE,warning = FALSE, message = FALSE}
# import planning district and housing data
district <- 
  st_read("https://raw.githubusercontent.com/ObjQIAN/Airbnb_AMS/main/data/neighbourhoods.geojson") %>%
  dplyr::select(neighbourhood, geometry) %>% 
  st_transform('EPSG:7415')

listings <- 
  st_read("https://raw.githubusercontent.com/ObjQIAN/Airbnb_AMS/main/data/listings.csv") %>%
  dplyr::select(-neighbourhood_group) %>%  # delete the column that has no value
  st_as_sf(coords=c("longitude","latitude"), crs=4326) %>%
  st_transform('EPSG:7415')

ggplot()+
  geom_sf(data = listings)+
  geom_sf(data = district , fill = NA)
```

#### (2) Load neighbourhood property characteristics

characteristics | point data
    -   `high-rise`: high-rise buildings built in each census tract
    -   `green-roof`: green roofs with its surface in each census tract
    -   `wall art`: number of wall art in each census tract
    -   `market`: Number of market in each census tract
    -   `swimming water`: Number of swimming pool in each census tract
characteristics | line data
    -   `tram_metro`: trams and metros in the whole city
characteristics | plane data
    -   `flood`：flood area in each census tract
    -   `parking`: parking lot in each census tract
    
```{r,results = FALSE,warning = FALSE, message = FALSE}
# 1.Load high-rise data with 3 attributes: height, year, and geometry
high_rise.sf <- 
  st_read("https://maps.amsterdam.nl/open_geodata/geojson_latlng.php?KAARTLAAG=HOOGBOUW_PUNT&THEMA=hoogbouw") %>%
  dplyr::select(Hoogte, Jaar, geometry) %>% 
  rename(
    height = Hoogte,
    year = Jaar
  )%>%
  st_transform('EPSG:7415')

# 2.Load green roof data with 2 attributes
green_roof.sf <- 
  st_read("https://maps.amsterdam.nl/open_geodata/geojson_latlng.php?KAARTLAAG=GROENE_DAKEN&THEMA=groene_daken") %>%
  dplyr::select(Oppervlakte_m2, geometry) %>% 
  rename(surface = Oppervlakte_m2)%>%
  st_transform('EPSG:7415')

# 3.Load wall art data
wall_art.sf <- st_read('https://maps.amsterdam.nl/open_geodata/geojson_latlng.php?KAARTLAAG=WANDKUNST&THEMA=wandkunst')%>%
  dplyr::select(geometry) %>%
  st_transform('ESRI:102729')

# 4.Load market data
market.sf <- st_read('https://maps.amsterdam.nl/open_geodata/geojson_latlng.php?KAARTLAAG=MARKTEN&THEMA=markten')%>%
  dplyr::select(geometry) %>% 
  st_transform('ESRI:102729')

# 5.Load swimming water data
swimming.sf <- st_read('https://maps.amsterdam.nl/open_geodata/geojson_latlng.php?KAARTLAAG=ZWEMWATER&THEMA=zwemwater')%>%
  dplyr::select(geometry) %>% 
  st_transform('ESRI:102729')

# 6.Load tram and metro data
tram_metro.sf <- st_read('https://maps.amsterdam.nl/open_geodata/geojson_latlng.php?KAARTLAAG=TRAMMETRO_LIJNEN_2022&THEMA=trammetro')%>%
  dplyr::select(Modaliteit, geometry) %>% 
  rename(modality = Modaliteit)%>%
  st_transform('ESRI:102729')

# 7.Load flood data
flood.sf <- st_read('https://maps.amsterdam.nl/open_geodata/geojson_latlng.php?KAARTLAAG=KLIMAAT_OVERSTROMING&THEMA=klimaatadaptatie')%>%
  dplyr::select(geometry) %>%
  st_transform('ESRI:102729')

# 8.Load parking pressure data
parking.sf <- st_read('https://maps.amsterdam.nl/open_geodata/geojson_latlng.php?KAARTLAAG=PARKEERDRUK_BUURTEN&THEMA=parkeerdruk')%>%
  dplyr::select(geometry) %>% 
  st_transform('ESRI:102729')

```

### 2.1.2 Feature Engineering

#### (3) Amendity data

```{r}
# 1.high-rise
listings$high_rise.Buffer <- listings %>% 
    st_buffer(660) %>% 
    aggregate(mutate(high_rise.sf, counter = 1),., sum) %>%
    pull(counter)
nhoods <-
  nhoods %>% 
  mutate(
    landmark_nn1 = nn_function(st_coordinates(st_centroid(nhoods)), st_coordinates(st_centroid(high_rise.sf)), 1),
    landmark_nn2 = nn_function(st_coordinates(st_centroid(nhoods)), st_coordinates(st_centroid(high_rise.sf)), 2), 
    landmark_nn3 = nn_function(st_coordinates(st_centroid(nhoods)), st_coordinates(st_centroid(high_rise.sf)), 3), 
    landmark_nn4 = nn_function(st_coordinates(st_centroid(nhoods)), st_coordinates(st_centroid(high_rise.sf)), 4), 
    landmark_nn5 = nn_function(st_coordinates(st_centroid(nhoods)), st_coordinates(st_centroid(high_rise.sf)), 5))
nhoods %>%
  st_drop_geometry() %>%
  dplyr::select(price, starts_with("high_rise_")) %>%
  filter(price <= 1000000) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_point(size = .5) + 
     geom_smooth(data = . %>% filter(price > 0), method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, nrow = 1, scales = "free") +
     labs(title = "Price as a function of high-rise") +
     plotTheme()

```